---
title: "ASF Community Structure Analysis"
author: "Joao Carlos Gomes Neto"
date: "September 26, 2016"
output: word_document
---

This file contains all the scripts for the ASF community structure analysis.
Thus ASF composition refers to the community structure of this microbiota.

There are three questions to be answered:

1) Do host genetics, pathobiont, and DSS status alter the ASF composition? Answered
2) Does the order of colonization alter the ASF composition (only one genotype = C3H/HeN) ? Answered 
3) Does the parental generation (G1 vs G2) alter the ASF composition (only one genotype = C3H/HeN) ? Answered
4) Whithin the diseased group (H bilis-ASF-DSS) in each genotype, is there a correlation between the pathobiont and ASF members abundance?
5) Whithin the non- and diseased group (H bilis-ASF-DSS) in C3H/HeN mice, is there a correlation between the pathobiont and ASF members abundance?

H. bilis = pathobiont
ASF = microbial community comprised of 8 bacteria that are not pathogenic
DSS = sulphated carbohydrate that induces intestinal epithelial lesions and release of IL-1B by macrophages in the lamina propria of cecum and colon (in our system it is used in a sub-pathological dose)
host genotype = C57BL/6 and C3H/HeN wild type, and RAG1KO in the C57BL/6 background

##########################################################################

Data 1 in the continuous format 

1) Do host genetics, pathobiont, and DSS status alter the ASF composition?

microbiota was assembled as follows:
ASF from birth (Vertical transmission)
H. bilis (pathobiont) later in life as an adult

```{r, echo=TRUE}
library(permute)
library(vegan)
library(lattice)
library(ggplot2)
library(ggfortify)
library(scales)
setwd("~/Documents/pathobiont paper/communitystructure")
datanew1<-read.csv("data1cont.csv")
sum(is.na(datanew1)) #checking for NA
str(datanew1)
head(datanew1)
tail(datanew1)
#raw data is comprised of the total number of each ASF taxon per gram of cecal content as quantified by species-specific qPCR assays

dfn1 <- datanew1[c(5:12)]
str(dfn1)
plot(dfn1)
sd(dfn1$ASF_356)
sd(dfn1$ASF_360)
sd(dfn1$ASF_361)
sd(dfn1$ASF_457)
sd(dfn1$ASF_492)
sd(dfn1$ASF_500)
sd(dfn1$ASF_502)
sd(dfn1$ASF_519)

#PCA analysis - since the variance is variable across all ASF the variables will be standardized to decrease their singular impact on the principal components (that will be applied to all datasets). Yet all ASF were measured in the same unit
pca1<-prcomp(dfn1, scale= TRUE) 
summary(pca1)
pca1
plot(pca1, type='l', main="Scree plot")
#pca.save<-princomp(dfn1, cor = TRUE, scores = TRUE)
#pca.save
#summary(pca.save)


p1<-autoplot(prcomp(dfn1, scale=TRUE), data = datanew1, colour = 'genotype', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (46.48%)", ylab="PC2 (14.83%)")
p2<-autoplot(prcomp(dfn1, scale=TRUE), data = datanew1, colour = 'dss', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (46.48%)", ylab="PC2 (14.83%)")
p3<-autoplot(prcomp(dfn1, scale=TRUE), data = datanew1, colour = 'pathobiont', loadings= TRUE, loadings.label = TRUE, frame= TRUE, frame.type= 't', xlab="PC1 (46.48%)", ylab="PC2 (14.83%)")
p4<-autoplot(prcomp(dfn1, scale=TRUE), data = datanew1, colour = 'groups', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (46.48%)", ylab="PC2 (14.83%)")
new('ggmultiplot', plots = list(p1, p2, p3, p4))
#p1
#p2
#p3
#p4


#dataframe from wide to long format for relative abundance plot
library(tidyr)
datalong1 <- gather(datanew1, taxa, abundance, ASF_356:ASF_519, factor_key=TRUE)
head(datalong1)
str(datalong1)

# calculate proportions
library(plyr)
require(plyr)
datalong2 <- ddply(datalong1, .(groups, id, taxa))
head(datalong2)

datalong3<-ddply(datalong2, .(groups, id), transform, total=sum(abundance))
head(datalong3)

datalong3$proportion<-datalong3$abundance/datalong3$total
head(datalong3, 30)
testnew<-datalong3[1:8,]
testnew
sum(testnew$proportion)
testnew1<-datalong3[9:16,]
testnew1
sum(testnew1$proportion)

#relative abundances for each ASF considering the total number of bacteria per gram of cecal content
require(ggplot2)
p <- ggplot(data = datalong3, aes(x=groups, y=proportion)) 
p <- p + geom_boxplot(aes(fill = taxa))
p <- p + geom_point(aes(y=proportion, group=taxa), position = position_dodge(width=0.75))
p <- p + facet_wrap( ~ taxa, scales="fixed", ncol=2)
p <- p + xlab("Groups") + ylab("Proportion") 
p <- p + guides(fill=guide_legend(title="ASF Taxa"))
p <- p + theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

#Permanova analysis to decompose the variance and explain the ASF community structure
set.seed(44)
bc<-vegdist(dfn1, method="bray", binary=FALSE, na.rm=TRUE) 
#bc
set.seed(104)
ada=adonis(bc~groups, data=datanew1, permutations=999)
ada
set.seed(144)
ad=adonis(bc~genotype*dss*pathobiont, data=datanew1, permutations=999)
ad


# ANOSIM 

library(vegan)
anosim1 <- vegdist(dfn1,method="bray", binary=FALSE)
attach(datalong1)
anosim2 <- anosim(anosim1, groups)
summary(anosim2)
par(mar = c(7,7,7,7))
plot(anosim2, col=terrain.colors(5), horizontal=FALSE, ylab="Dissimilarity Ranks", axes= FALSE)
box()
axis(2,
     las=2)
names1a<-c("Between", "B6DSS", "B6Hb","B6HbDSS",
          "B6NoDSS", "C3HbDSS", "C3hHb","C3hHbDSS",
          "C3hNoDSS","RAGDSS", "RAGHb","RAGHbDSS",
          "RAGNoDSS")
axis(1,at=1:13, labels=names1a,
     las=2, cex.axis=0.8) 
#Analysis of homogeneity of the Bray-curtis distances using the betadisper function 
#objective :analysis of multivariate homogeneity of group dispersions (variances). betadisper is a multivariate analogue of Levene's test for homogeneity of variances
#I modified the code to use Bray-curtis distances instead of Euclidean's
#"One measure of multivariate dispersion (variance) for a group of samples is to calculate the average distance of group members to the group centroid or spatial median in multivariate space. To test if the dispersions (variances) of one or more groups are different, the distances of group members to the group centroid are subject to ANOVA. This is a multivariate analogue of Levene's test for homogeneity of variances if the distances between group members and group centroids is the Euclidean distance" (copied from vinnette http://cc.oulu.fi/~jarioksa/softhelp/vegan/html/betadisper.html).
par(mfrow=c(1,1))
mod <- with(datanew1, betadisper(bc, groups))
mod
plot(mod, main= "All Groups")
op <- par(mar = c(4,4,4,4) + 0.1)
boxplot(mod, cex.axis = 0.8, main= "All Groups", axes=TRUE,
        col=terrain.colors(4))
#box()
#axis(2,las=2)
#names1a<-c("B6DSS", "B6Hb","B6HbDSS",
          #"B6NoDSS", "C3HDSS", "C3hHb","C3hHbDSS",
         # "C3hNoDSS","RAGDSS", "RAGHb","RAGHbDSS",
         # "RAGNoDSS")
#axis(1,at=1:12, labels=names1a,
     #las=2, cex.axis=0.8) 
par(op)
anova(mod)
permutest(mod)
TukeyHSD(mod)# provide the p-values for group comparisons 
par(mfrow=c(2,2))
mod1 <- with(datanew1, betadisper(bc, genotype))
mod1
plot(mod1, main= "Genotype")
boxplot(mod1, main= "Genotype", ylim= c(0,1))
anova(mod1)
permutest(mod1)
TukeyHSD(mod1)# provide the p-values for group comparisons 

mod2 <- with(datanew1, betadisper(bc, dss))
mod2
plot(mod2, main= "DSS status")
boxplot(mod2, main= "DSS status", ylim= c(0,1))
anova(mod2)
permutest(mod2)
TukeyHSD(mod2)# provide the p-values for group comparisons 

mod3 <- with(datanew1, betadisper(bc, pathobiont))
mod3
plot(mod3, main= "Pathobiont colonization status")
boxplot(mod3, main= "Pathobiont colonization status", ylim= c(0,1))
anova(mod3)
permutest(mod3)
TukeyHSD(mod3)# provide the p-values for group comparisons 

##########################################################

#C3H/HeN

#1) need to subset the dataset 
datanew1
datac3h<-datanew1[c(1:44),]
datac3h
sub1 <- datac3h[c(5:12)]
str(sub1)
pcac3h<-prcomp(sub1, scale= TRUE) 
summary(pcac3h)
pcac3h
plot(pcac3h, type='l', main="Scree plot")
plot1<-autoplot(prcomp(sub1, scale=TRUE), data = datac3h, colour = 'groups', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (54.33%)", ylab="PC2 (21.22%)")
plot2<-autoplot(prcomp(sub1, scale=TRUE), data = datac3h, colour = 'dss', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (54.33%)", ylab="PC2 (21.22%)")
plot3<-autoplot(prcomp(sub1, scale=TRUE), data = datac3h, colour = 'pathobiont', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (54.33%)", ylab="PC2 (21.22%)")
new('ggmultiplot', plots = list(plot1, plot2, plot3))

#Permanova analysis to decompose the variance and explain the ASF community structure
set.seed(4454)
bc1a<-vegdist(sub1, method="bray", binary=FALSE, na.rm=TRUE) 
#bc
set.seed(1042)
ada1=adonis(bc1a~groups, data=datac3h, permutations=999)
ada1
set.seed(1442)
ad1=adonis(bc1a~dss*pathobiont, data=datac3h, permutations=999)
ad1


# ANOSIM 
library(vegan)
#dataframe from wide to long format for relative abundance plot
library(tidyr)
datalongc3h <- gather(datac3h, taxa, abundance, ASF_356:ASF_519, factor_key=TRUE)
head(datalongc3h)
str(datalongc3h)
anosimc3h <- vegdist(sub1,method="bray", binary=FALSE)
attach(datalongc3h)
anosim2 <- anosim(anosimc3h, groups)
summary(anosim2)

#BC variance
set.seed(4432)
bc.1<-vegdist(sub1, method="bray", binary=FALSE, na.rm=TRUE)
mod.fit1 <- with(datac3h, betadisper(bc.1, groups))
mod.fit1
plot(mod.fit1, main= "groups")
boxplot(mod.fit1, main= "groups", ylim= c(0,1))
anova(mod.fit1)
permutest(mod.fit1)
TukeyHSD(mod.fit1)# provide the p-values for group comparisons 
##########################################################
#C57BL/6

#1) need to subset the dataset 
datab6<-datanew1[c(45:101),]
datab6
str(datab6)
sub2 <- datab6[c(5:12)]
str(sub2)
pcab6<-prcomp(sub2, scale= TRUE) 
summary(pcab6)
pcab6
plot(pcab6, type='l', main="Scree plot")
plot1a<-autoplot(prcomp(sub2, scale=TRUE), data = datab6, colour = 'groups', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (35.79%)", ylab="PC2 (21.93%)")
plot2a<-autoplot(prcomp(sub2, scale=TRUE), data = datab6, colour = 'dss', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (35.79%)", ylab="PC2 (21.93%)")
plot3a<-autoplot(prcomp(sub2, scale=TRUE), data = datab6, colour = 'pathobiont', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (35.79%)", ylab="PC2 (21.93%)")
new('ggmultiplot', plots = list(plot1a, plot2a, plot3a))

#Permanova analysis to decompose the variance and explain the ASF community structure
set.seed(3495)
b6a<-vegdist(sub2, method="bray", binary=FALSE, na.rm=TRUE) 
#bc
set.seed(0948)
mod6a=adonis(b6a~groups, data=datab6, permutations=999)
mod6a
set.seed(5748)
mod6b=adonis(b6a~dss*pathobiont, data=datab6, permutations=999)
mod6b


# ANOSIM 
library(vegan)
#dataframe from wide to long format for relative abundance plot
library(tidyr)
datalongb6 <- gather(datab6, taxa, abundance, ASF_356:ASF_519, factor_key=TRUE)
head(datalongb6)
str(datalongb6)
anosimb6a <- vegdist(sub2,method="bray", binary=FALSE)
attach(datalongb6)
anosimb6b <- anosim(anosimb6a, groups)
summary(anosimb6b)

#BC variance
set.seed(4757)
bc.1a<-vegdist(sub2, method="bray", binary=FALSE, na.rm=TRUE)
mod.fit1a<- with(datab6, betadisper(bc.1a, groups))
mod.fit1a
plot(mod.fit1a, main= "groups")
boxplot(mod.fit1a, main= "groups", ylim= c(0,1))
anova(mod.fit1a)
permutest(mod.fit1a)
TukeyHSD(mod.fit1a)# provide the p-values for group comparisons 
##########################################################
#RAG1-/-
#1) need to subset the dataset 
datarag<-datanew1[c(102:142),]
datarag
rag1 <- datarag[c(5:12)]
str(rag1)
pcarag<-prcomp(rag1, scale= TRUE) 
summary(pcarag)
pcarag
plot(pcarag, type='l', main="Scree plot")
plot1b<-autoplot(prcomp(rag1, scale=TRUE), data = datarag, colour = 'groups', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (31.99%)", ylab="PC2 (21.24%)")
plot2b<-autoplot(prcomp(rag1, scale=TRUE), data =datarag, colour = 'dss', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (31.99%)", ylab="PC2 (21.24%)")
plot3b<-autoplot(prcomp(rag1, scale=TRUE), data = datarag, colour = 'pathobiont', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (31.99%)", ylab="PC2 (21.24%)")
new('ggmultiplot', plots = list(plot1b, plot2b, plot3b))

#Permanova analysis to decompose the variance and explain the ASF community structure
set.seed(3567)
bc1a1<-vegdist(rag1, method="bray", binary=FALSE, na.rm=TRUE) 
#bc
set.seed(9056)
ada11=adonis(bc1a1~groups, data=datarag, permutations=999)
ada11
set.seed(5894)
ad12=adonis(bc1a1~dss*pathobiont, data=datarag, permutations=999)
ad12


# ANOSIM 
library(vegan)
#dataframe from wide to long format for relative abundance plot
library(tidyr)
datalongrag <- gather(datarag, taxa, abundance, ASF_356:ASF_519, factor_key=TRUE)
head(datalongrag)
str(datalongrag)
anosimrag <- vegdist(rag1,method="bray", binary=FALSE)
attach(datalongrag)
anosimrag1 <- anosim(anosimrag, groups)
summary(anosimrag1)

#BC variance
set.seed(4563)
bc.rag<-vegdist(rag1, method="bray", binary=FALSE, na.rm=TRUE)
mod.fit1bb <- with(datarag, betadisper(bc.rag, groups))
mod.fit1bb
plot(mod.fit1bb, main= "groups")
boxplot(mod.fit1bb, main= "groups", ylim= c(0,1))
anova(mod.fit1bb)
permutest(mod.fit1bb)
TukeyHSD(mod.fit1bb)# provide the p-values for group comparisons 
```

data 2 - Order of colonization between the pathobiont and ASF community
2) Does the order of colonization alter the ASF composition?
all data comes from C3H/HeN mice 
```{r, echo=TRUE}
data2<-read.csv("data2cont.csv")
sum(is.na(data2)) #checking for NA
str(data2)
head(data2)
tail(data2)
data2a<-na.omit(data2)
str(data2a)
sum(is.na(data2a))
table(data2a$groups)
df2 <- data2a[c(5:12)]
str(df2)

#PCA analysis 
pca2<-prcomp(df2, scale= TRUE) 
summary(pca2)
pca2
plot(pca2, type='l', main="Scree plot")


p5<-autoplot(prcomp(df2, scale=TRUE), data = data2a, colour = 'asf', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (41.21%)", ylab="PC2 (19.22%)")
p6<-autoplot(prcomp(df2, scale=TRUE), data = data2a, colour = 'dss', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (41.21%)", ylab="PC2 (19.22%)")
p7<-autoplot(prcomp(df2, scale=TRUE), data = data2a, colour = 'pathobiont', loadings= TRUE, loadings.label = TRUE, frame= TRUE, frame.type= 't', xlab="PC1 (41.21%)", ylab="PC2 (19.22%)")
p8<-autoplot(prcomp(df2, scale=TRUE), data = data2a, colour = 'TREATMENTS', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (41.21%)", ylab="PC2 (19.22%)", label.size = 50, size = 3, label.n = 30)+
theme(axis.text=element_text(size=30, family="Arial"),
        axis.title=element_text(size=30,face="bold", family="Arial"),
        legend.text=element_text(size=24, family="Arial"),
        legend.title=element_text(size=24,face="bold", family="Arial"))
p8

p8a
new('ggmultiplot', plots = list(p8, p11a))
#p5
#p6
#p7
#p8

#dataframe from wide to long format for relative abundance plot
library(tidyr)
datalong2a <- gather(data2a, taxa, abundance, ASF_356:ASF_519, factor_key=TRUE)
head(datalong2a)
str(datalong2a)

# calculate proportions
library(plyr)
require(plyr)
datalong2b <- ddply(datalong2a, .(TREATMENTS, id, taxa))
head(datalong2b)

datalong2c<-ddply(datalong2b, .(TREATMENTS, id), transform, total=sum(abundance))
head(datalong2c)

datalong2c$proportion<-datalong2c$abundance/datalong2c$total
head(datalong2c, 20)
testnew<-datalong2c[1:8,]
testnew
sum(testnew$proportion)
testnew1<-datalong2c[9:16,]
testnew1
sum(testnew1$proportion)

#relative abundances for each ASF considering the total number of bacteria per gram of cecal content
require(ggplot2)
p <- ggplot(data = datalong2c, aes(x=TREATMENTS, y=proportion)) 
p <- p + geom_boxplot(aes(fill = taxa))
p <- p + geom_point(aes(y=proportion, group=taxa), position = position_dodge(width=0.75))
p <- p + facet_wrap( ~ taxa, scales="fixed", ncol=2)
p <- p + xlab("Groups") + ylab("Proportion") 
p <- p + guides(fill=guide_legend(title="ASF Taxa"))
p <- p + theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

#Permanova analysis to decompose the variance and explain the ASF community structure
set.seed(4490)
bc2<-vegdist(df2, method="bray", binary=FALSE, na.rm=TRUE) 
pca2bb<-prcomp(bc2, scale= TRUE) 
summary(pca2bb)
p8bb<-autoplot(prcomp(bc2, scale=TRUE), data = data2a, colour = 'TREATMENTS', loadings= FALSE, loadings.label = FALSE, frame = TRUE, frame.type= 't', xlab="PC1 (41.21%)", ylab="PC2 (19.22%)", label.size = 50, size = 3, label.n = 30)+
theme(axis.text=element_text(size=20, family="Arial"),
        axis.title=element_text(size=20,face="bold", family="Arial"),
        legend.text=element_text(size=16, family="Arial"),
        legend.title=element_text(size=16,face="bold", family="Arial"))
p8bb
#bc
set.seed(1041)
ada2=adonis(bc2~TREATMENTS, data=data2a, permutations=999)
ada2
set.seed(1233)
ad2=adonis(bc2~asf*dss*pathobiont, data=data2a, permutations=999)
ad2

#Analysis of homogeneity of the Bray-curtis distances using the betadisper function 
#objective :analysis of multivariate homogeneity of group dispersions (variances). betadisper is a multivariate analogue of Levene's test for homogeneity of variances

mod2a <- with(data2a, betadisper(bc2, TREATMENTS))
mod2a
plot(mod2a, main= "All Groups")
op <- par(mar = c(4,4,4,4) + 0.1)
boxplot(mod2a, cex.axis = 0.8, main= "All Groups", ylim= c(0,1), col=terrain.colors(2))
par(op)
anova(mod2a)
permutest(mod2a)
TukeyHSD(mod2a)# provide the p-values for group comparisons 

mod2b <- with(data2a, betadisper(bc2, asf))
mod2b
plot(mod2b, main= "Timing of ASF colonization")
boxplot(mod2b, main= "Timing of ASF colonization", ylim= c(0,1))
anova(mod2b)
permutest(mod2b)
TukeyHSD(mod2b)# provide the p-values for group comparisons 

mod2c <- with(data2a, betadisper(bc2, dss))
mod2c
plot(mod2c, main= "DSS status")
boxplot(mod2c, main= "DSS status", ylim= c(0,1))
anova(mod2c)
permutest(mod2c)
TukeyHSD(mod2c)# provide the p-values for group comparisons 

mod2d <- with(data2a, betadisper(bc2, pathobiont))
mod2d
plot(mod2d, main= "Timing of Pathobiont colonization")
boxplot(mod2d, main= "Timing of Pathobiont colonization", ylim= c(0,1))
anova(mod2d)
permutest(mod2d)
TukeyHSD(mod2d)# provide the p-values for group comparisons 

# ANOSIM 
library(vegan)
#dataframe from wide to long format for relative abundance plot
library(tidyr)

anosim11<- vegdist(df2,method="bray", binary=FALSE)
attach(datalong2a)
anosim12 <- anosim(anosim11, TREATMENTS)
summary(anosim12)
plot(anosim12)
```



data 3 - Generation and/or DSS effect once the pathobiont is established
3) Does the parental generation (G1 vs G2 vs G3) alter the ASF composition?

dataset comes from C3H/HeN mice colonized with H. bilis and ASF from birth
```{r, echo=TRUE}

data3<-read.csv("data3cont.csv")
sum(is.na(data3)) #checking for NA
str(data3)
head(data3)
tail(data3)
data3a<-na.omit(data3)
str(data3a)
sum(is.na(data3a))
data3a$generation=factor(data3a$generation)
str(data3a)
table(data3a$groups)
#PCA analysis
df3 <- data3a[c(6:13)]
str(df3)
pca3<-prcomp(df3, scale= TRUE)  #cor=TRUE
summary(pca3)
pca3
plot(pca3, type='l', main = "Scree plot")


p9<-autoplot(prcomp(df3, scale= TRUE), data = data3a, colour = 'generation', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (35.73%)", ylab="PC2 (23%)")
p10<-autoplot(prcomp(df3, scale = TRUE), data = data3a, colour = 'dss', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (35.73%)", ylab="PC2 (23%)")
p11<-autoplot(prcomp(df3, scale = TRUE), data = data3a, colour = 'TREATMENTS', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (35.73%)", ylab="PC2 (23%)",
label.size = 50, size = 3, label.n = 30) +
theme(axis.text=element_text(size=30, family="Arial"),
        axis.title=element_text(size=30,face="bold", family="Arial"),
        legend.text=element_text(size=24, family="Arial"),
        legend.title=element_text(size=24,face="bold", family="Arial"))



p11a<-p11+theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold"),
        legend.text=element_text(size=16),
        legend.title=element_text(size=16,face="bold"))
p11a
#p11+theme_bw()
new('ggmultiplot', plots = list(p9, p10, p11))
new('ggmultiplot', plots = list(p8a, p11a))

#p9
#p10
#p11
#p11a<-p11 + theme(panel.background = element_rect(fill='white', colour='black'))
#p11a + theme(panel.grid.major = element_rect(color='black')
           #  , panel.grid.minor = element_blank())

#dataframe from wide to long format for relative abundance plot
library(tidyr)
datalong3a <- gather(data3a, taxa, abundance, ASF_356:ASF_519, factor_key=TRUE)
head(datalong3a)
tail(datalong3a)
str(datalong3a)

# calculate proportions
library(plyr)
require(plyr)
datalong3b <- ddply(datalong3a, .(TREATMENTS, id, taxa))
head(datalong3b)

datalong3c<-ddply(datalong3b, .(TREATMENTS, id), transform, total=sum(abundance))
#head(datalong3c)

datalong3c$proportion<-datalong3c$abundance/datalong3c$total
head(datalong3c, 20)
testnew3<-datalong3c[1:8,]
testnew3
sum(testnew3$proportion)
testnew3<-datalong3c[9:16,]
testnew3
sum(testnew3$proportion)

#relative abundances for each ASF considering the total number of bacteria per gram of cecal content
require(ggplot2)
p <- ggplot(data = datalong3c, aes(x=TREATMENTS, y=proportion)) 
p <- p + geom_boxplot(aes(fill = taxa))
p <- p + geom_point(aes(y=proportion, group=taxa), position = position_dodge(width=0.75))
p <- p + facet_wrap( ~ taxa, scales="fixed", ncol=2)
p <- p + xlab("Groups") + ylab("Proportion") 
p <- p + guides(fill=guide_legend(title="ASF Taxa"))
p <- p + theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

#Permanova analysis to decompose the variance and explain the ASF community structure
set.seed(445)
bc3<-vegdist(df3, method="bray", binary=FALSE, na.rm=TRUE) 
#bc
set.seed(1045)
ada4=adonis(bc3~TREATMENTS, data=data3a, permutations=999)
ada4
set.seed(1443)
ad4=adonis(bc3~generation*dss, data=data3a, permutations=999)
ad4
set.seed(1442)
ad5=adonis(bc3~generation+dss, data=data3a, permutations=999)
ad5
anosim(df3, TREATMENTS,permutations = 999, distance = "bray")
set.seed(569)
library(vegan)
data(dune)
data(dune.env)
dune.dist <- vegdist(df3)
attach(datalong3a)
dune.ano <- anosim(dune.dist, TREATMENTS)
summary(dune.ano)
par(mar = c(7,7,7,7))
plot(dune.ano, col=terrain.colors(5), horiz=FALSE, ylab="Dissimilarity Ranks", axes= FALSE)
box()
axis(2,
     las=2)
names1<-c("Between", "HbASFbirth1", "HbASFbirth1DSS","HbASFbirth2",
          "HbASFbirth2DSS","HbASFbirth3", "HbASFbirth3DSS")
axis(1,at=1:7, labels=names1,
     las=2, cex.axis=0.8) 
# ANOSIM 
library(vegan)
#dataframe from wide to long format for relative abundance plot
library(tidyr)

anosimG3<- vegdist(df3,method="bray", binary=FALSE)
attach(datalong3a)
anosimG4 <- anosim(anosimG3, TREATMENTS)
summary(anosimG4)
plot(anosimG4)
#Analysis of homogeneity of the Bray-curtis distances using the betadisper function 
#objective :analysis of multivariate homogeneity of group dispersions (variances). betadisper is a multivariate analogue of Levene's test for homogeneity of variances

mod3a <- with(data3a, betadisper(bc3, TREATMENTS), type=c("centroid"))
mod3a
plot(mod3a, main= "All Groups")
op <- par(mar = c(4,4,4,4) + 0.1)
boxplot(mod3a, cex.axis = 0.8, main= "All Groups", ylim= c(0,1))
par(op)
anova(mod3a)
permutest(mod3a)
TukeyHSD(mod3a)# provide the p-values for group comparisons 

mod3b <- with(data3a, betadisper(bc3, generation))
mod3b
plot(mod3b, main= "Generation")
boxplot(mod3b, main= "Generation", ylim= c(0,1))
anova(mod3b)
permutest(mod3b)
TukeyHSD(mod3b)# provide the p-values for group comparisons 

mod3c <- with(data3a, betadisper(bc3, dss))
mod3c
plot(mod3c, main= "DSS status")
boxplot(mod3c, main= "DSS status", ylim= c(0,1))
anova(mod3c)
anova(mod3c)
permutest(mod3c)
TukeyHSD(mod3c)# provide the p-values for group comparisons 
```

4)ASF birth Hb later - community structure analysis

- PCA plot using raw abundances
- Permanova
- Anosim
- Betadisper

```{r, echo=TRUE}
mod1<-read.csv("data6cont.csv")
sum(is.na(mod1)) #checking for NA
str(mod1)
head(mod1)
tail(mod1)
mod2<-na.omit(mod1)
str(mod2)
sum(is.na(mod2))


#PCA analysis
dataPCA <- mod2[c(2:9)]
str(dataPCA)
pcamod2<-prcomp(dataPCA, scale= TRUE)  #cor=TRUE
summary(pcamod2)
pcamod2
plot(pcamod2, type='l', main = "Scree plot")



plotmod2<-autoplot(prcomp(dataPCA, scale = TRUE), data = mod2, colour = 'TREATMENTS', loadings= TRUE, loadings.label = TRUE, frame = TRUE, frame.type= 't', xlab="PC1 (54.33%)", ylab="PC2 (21.22%)",
label.size = 50, size = 3, label.n = 30) +
theme(axis.text=element_text(size=30, family="Arial"),
        axis.title=element_text(size=30,face="bold", family="Arial"),
        legend.text=element_text(size=20, family="Arial"),
        legend.title=element_text(size=24,face="bold", family="Arial"))


#dataframe from wide to long format for relative abundance plot
library(tidyr)
mod3 <- gather(mod2, taxa, abundance, ASF_356:ASF_519, factor_key=TRUE)
head(mod3)
tail(mod3)
str(mod3)

# calculate proportions
library(plyr)
require(plyr)
mod4 <- ddply(mod3, .(TREATMENTS, id, taxa))
head(mod4)

mod5<-ddply(mod4, .(TREATMENTS, id), transform, total=sum(abundance))
#head(datalong3c)

mod5$proportion<-mod5$abundance/mod5$total
head(mod5)
testnew3<-mod5[1:8,]
testnew3
sum(testnew3$proportion)
testnew3<-mod5[9:16,]
testnew3
sum(testnew3$proportion)

#relative abundances for each ASF considering the total number of bacteria per gram of cecal content
require(ggplot2)
p <- ggplot(data = mod5, aes(x=TREATMENTS, y=proportion)) 
p <- p + geom_boxplot(aes(fill = taxa))
p <- p + geom_point(aes(y=proportion, group=taxa), position = position_dodge(width=0.75))
p <- p + facet_wrap( ~ taxa, scales="fixed", ncol=2)
p <- p + xlab("TREATMENTS") + ylab("Proportion") 
p <- p + guides(fill=guide_legend(title="ASF Taxa"))
p <- p + theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

#Permanova analysis to decompose the variance and explain the ASF community structure
set.seed(4456)
pm1<-vegdist(dataPCA, method="bray", binary=FALSE, na.rm=TRUE) 
#bc
set.seed(1045)
pm2=adonis(pm1~TREATMENTS, data=mod2, permutations=999)
pm2


# ANOSIM 
library(vegan)
#dataframe from wide to long format for relative abundance plot
library(tidyr)

an1<- vegdist(dataPCA,method="bray", binary=FALSE)
attach(mod3)
an2 <- anosim(an1, TREATMENTS)
summary(an2)
plot(an2)

#Analysis of homogeneity of the Bray-curtis distances using the betadisper function 
#objective :analysis of multivariate homogeneity of group dispersions (variances). betadisper is a multivariate analogue of Levene's test for homogeneity of variances

bet1 <- with(mod2, betadisper(an1, TREATMENTS), type=c("centroid"))
bet1
plot(bet1, main= "All Groups")
boxplot(bet1, cex.axis = 0.8, main= "All Groups", ylim= c(0,1))
anova(bet1)
permutest(bet1)
TukeyHSD(bet1)# provide the p-values for group comparisons 

 
```


5) Whithin the diseased group (H bilis-ASF-DSS) in each genotype, is there a correlation between the pathobiont and ASF members abundance?


```{r, echo=TRUE}

data4<-read.csv("data4cont.csv")
sum(is.na(data4)) #checking for NA
str(data4)
head(data4, 3)
tail(data4, 3)
data4a<-na.omit(data4)
str(data4a)
sum(is.na(data4a))
data4a=data4[,-c(1:5)]
str(data4a)
plot(data4a)

#subset C3H

data4b=data4[c(1:11),]
str(data4b)
data4b
sum(is.na(data4b))
data4b=na.omit(data4b)
sum(is.na(data4b))
datasub1a=data4b[,-c(1:5)]
str(datasub1a)
plot(datasub1a)

#Spearman correlation and heat map C3H

cormat1a<-round(cor(datasub1a, method="spearman", use = "complete.obs"),2)
heatmap(cormat1a)
head(cormat1a)
plot(pathobiont~ASF_356, data=datasub1a)
library(reshape2)
melted_cormat1a <- melt(cormat1a)
head(melted_cormat1a)

library(ggplot2)
ggplot(data = melted_cormat1a, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }

upper_tri1a<- get_upper_tri(cormat1a)
upper_tri1a


# Melt the correlation matrix
library(reshape2)
melted_cormat1b <- melt(upper_tri1a, na.rm = TRUE)
melted_cormat1b 
melted_cormat1b<-melted_cormat1b[order(melted_cormat1b$Var1), ]
melted_cormat1b

#subseting from correlation matrix
head(melted_cormat1b, 10)
melted_cormat1c=melted_cormat1b[1:9,]
melted_cormat1c

# Heatmap
library(ggplot2)
ggheatmap1<-ggplot(data = melted_cormat1c, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Spearman Correlation") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 20, hjust = 0.7))+
  theme(axis.text.y = element_text(size=20))+
 coord_fixed()

#print(ggheatmap)

ggheatmap2<-ggheatmap1 + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 12) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(1, 1),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 12, barheight = 0.8,
                title.position = "top", title.hjust = 0.5,
                title.theme= element_text(size = 20, angle= 0)))

ggheatmap2 + ggtitle(expression(paste(italic('H. bilis'),"(pathobiont)-ASF-1.5% DSS")))

######################################################################
#subset B6
data4c=data4[c(12:29),]
str(data4c)
data4c
sum(is.na(data4c))
data4c=na.omit(data4c)
sum(is.na(data4c))
datasub2a=data4c[,-c(1:5)]
str(datasub2a)
plot(datasub2a)

#Pearson correlation and heat map B6

cormat2a<-round(cor(datasub2a, method="spearman", use = "complete.obs"),2)
heatmap(cormat2a)
head(cormat2a)

library(reshape2)
melted_cormat2a <- melt(cormat2a)
head(melted_cormat2a)

library(ggplot2)
ggplot(data = melted_cormat2a, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }

upper_tri2a<- get_upper_tri(cormat2a)
upper_tri2a


# Melt the correlation matrix
library(reshape2)
melted_cormat2b <- melt(upper_tri2a, na.rm = TRUE)
melted_cormat2b 
melted_cormat2b<-melted_cormat2b[order(melted_cormat2b$Var1), ]
melted_cormat2b

#subseting from correlation matrix
head(melted_cormat2b, 10)
melted_cormat2c=melted_cormat2b[1:9,]
melted_cormat2c

# Heatmap
library(ggplot2)
ggheatmap2a<-ggplot(data = melted_cormat2c, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Spearman\nCorrelation") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 0.7))+
 coord_fixed()

#print(ggheatmap)

ggheatmap2b<-ggheatmap2a + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(1, 1),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))

ggheatmap2b + ggtitle(expression(paste(italic('H. bilis'),"(pathobiont)-ASF-2% DSS")))

######################################################################
#subset RAG1-/-

data4d=data4[c(30:41),]
str(data4d)
data4d
sum(is.na(data4d))
data4d=na.omit(data4d)
sum(is.na(data4d))
datasub3a=data4d[,-c(1:5)]
str(datasub3a)
plot(datasub3a)

#Pearson correlation and heat map RAG1-/-

cormat3a<-round(cor(datasub3a, method="spearman", use = "complete.obs"),2)
heatmap(cormat3a)
head(cormat3a)

library(reshape2)
melted_cormat3a <- melt(cormat3a)
head(melted_cormat3a)

library(ggplot2)
ggplot(data = melted_cormat3a, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }

upper_tri3a<- get_upper_tri(cormat3a)
upper_tri3a


# Melt the correlation matrix
library(reshape2)
melted_cormat3b <- melt(upper_tri3a, na.rm = TRUE)
melted_cormat3b 
melted_cormat3b<-melted_cormat3b[order(melted_cormat3b$Var1), ]
melted_cormat3b

#subseting from correlation matrix
head(melted_cormat3b, 10)
melted_cormat3c=melted_cormat3b[1:9,]
melted_cormat3c

# Heatmap
library(ggplot2)
ggheatmap3a<-ggplot(data = melted_cormat3c, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Spearman\nCorrelation") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 0.7))+
 coord_fixed()

#print(ggheatmap)

ggheatmap3b<-ggheatmap3a + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(1, 1),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))

ggheatmap3b + ggtitle(expression(paste(italic('H. bilis'),"(pathobiont)-ASF-2% DSS")))

c<-ggheatmap2b + ggtitle(expression(paste(italic('H. bilis'),"(pathobiont)-ASF-2% DSS")))+ 
      labs(x=" C57BL/6 - Cecal content bacteria")+ 
      theme(plot.title = element_text(size = 12))+
      theme(axis.title.x = element_text(size = 12))

d<-ggheatmap3b + ggtitle(expression(paste(italic('H. bilis'),"(pathobiont)-ASF-2% DSS")))+ 
      labs(x="RAG1KO - Cecal content bacteria")+ 
      theme(plot.title = element_text(size = 12))+
      theme(axis.title.x = element_text(size = 12))

library(gridExtra)
grid.arrange(c,d, ncol=2, clip=TRUE)

#######################################################################
#subset HBASFnoDSS C3H/HeN
data5a=data4[c(42:51),]
str(data5a)
data5a
sum(is.na(data5a))
data4d=na.omit(data5a)
sum(is.na(data5a))
datasub5a=data5a[,-c(1:5)]
str(datasub5a)
plot(datasub5a)

#Pearson correlation and heat map C3H

cormat5a<-round(cor(datasub5a, method="spearman", use = "complete.obs"),2)
heatmap(cormat5a)
head(cormat5a)

library(reshape2)
melted_cormat5a <- melt(cormat5a)
head(melted_cormat5a)

library(ggplot2)
ggplot(data = melted_cormat5a, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }

upper_tri5a<- get_upper_tri(cormat5a)
upper_tri5a


# Melt the correlation matrix
library(reshape2)
melted_cormat5b <- melt(upper_tri5a, na.rm = TRUE)
melted_cormat5b 
melted_cormat5b<-melted_cormat5b[order(melted_cormat5b$Var1), ]
melted_cormat5b

#subseting from correlation matrix
head(melted_cormat5b, 10)
melted_cormat5c=melted_cormat5b[1:9,]
melted_cormat5c

# Heatmap
library(ggplot2)
ggheatmap5a<-ggplot(data = melted_cormat5c, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Spearman Correlation") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 20, hjust = 0.7))+
  theme(axis.text.y = element_text(size=20))+
 coord_fixed()

#print(ggheatmap)

ggheatmap5b<-ggheatmap5a + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 12) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(1, 1),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 12, barheight = 0.8,
                title.position = "top", title.hjust = 0.5,   title.theme= element_text(size = 20, angle= 0)))


 

a<-ggheatmap5b + ggtitle(expression(paste(italic('H. bilis'),"(pathobiont)-ASF-no DSS")))+ 
      labs(x="C3H/HeN - Cecal content bacteria")+ 
      theme(plot.title = element_text(size = 22))+
      theme(axis.title.x = element_text(size = 22))


b<-ggheatmap2 + ggtitle(expression(paste(italic('H. bilis'),"(pathobiont)-ASF-1.5% DSS")))+ 
      labs(x="C3H/HeN - Cecal content bacteria")+ 
      theme(plot.title = element_text(size = 22))+
      theme(axis.title.x = element_text(size = 22))

#plist<-list(a,b)
#library(gridExtra)
#n <- length(plist)
#nCol <- floor(sqrt(n))
#do.call("grid.arrange", c(plist, ncol=nCol))
library(gridExtra)
grid.arrange(a,b, nrow=2, ncol=1, clip=TRUE)


#merging two matrices for HbASF no dss vs dss C3h

#matric1<-rbind(melted_cormat5c, melted_cormat1c)
#matric1

#group <- data.frame(name=c("HbASFnoDSS","HbASFnoDSS",
               #   "HbASFnoDSS","HbASFnoDSS","HbASFnoDSS","HbASFnoDSS",
               #   "HbASFnoDSS", "HbASFnoDSS", "HbASFnoDSS", 
               #   "HbASF1.5%DSS", "HbASF1.5%DSS", "HbASF1.5%DSS",
               #   "HbASF1.5%DSS", "HbASF1.5%DSS", "HbASF1.5%DSS",
               #   "HbASF1.5%DSS", "HbASF1.5%DSS", "HbASF1.5%DSS"))
#matric1b<-cbind(matric1, group)
#matric1b

#p <- ggplot( data=matric1b, aes(Var1, Var2)) + geom_tile(aes(fill = value), colour = "white") + scale_fill_gradient(low = "white", high = "steelblue")
#p <- p + facet_grid( .~group, scale="free")
#p

#dev.new(width=5, height=4)
#mat1 <- hmapmatric1b + facet_grid( .~name, scale="free")
#mat1


a<-ggheatmap5b + ggtitle(expression(paste(italic('H. bilis'),"(pathobiont)-ASF-no DSS")))+ 
      labs(x="C3H/HeN - Cecal content bacteria")+ 
      theme(plot.title = element_text(size = 12))+
      theme(axis.title.x = element_text(size = 12))



```

6) Whithin the non- and diseased group (H bilis-ASF-DSS) in C3H/HeN mice, is there a correlation between the pathobiont and ASF members abundance?
data from C3H/HeN mice 
HbASF no DSS vs DSS
cecal tissue associated bacteria


```{r, echo = TRUE}
data5<-read.csv("data5cont.csv")
sum(is.na(data5)) #checking for NA
str(data5)


#subset HbASF no DSS
head(data5, 9)
datasub6a=data5[c(1:8),]
datasub6a
sum(is.na(datasub6a))
str(datasub6a)
#now subset the quantitative variables out of HbASF
datasub6b=datasub6a[,-c(1:5)]
str(datasub6b)
plot(datasub6b)

#Pearson correlation and heat map HbASF no DSS

cormat6a<-round(cor(datasub6b, method="spearman", use = "complete.obs"),2)
heatmap(cormat6a)
head(cormat6a)

library(reshape2)
melted_cormat6a <- melt(cormat6a)
head(melted_cormat6a)

library(ggplot2)
ggplot(data = melted_cormat6a, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }

upper_tri6a<- get_upper_tri(cormat6a)
upper_tri6a


# Melt the correlation matrix
library(reshape2)
melted_cormat6b <- melt(upper_tri6a, na.rm = TRUE)
melted_cormat6b 
melted_cormat6b<-melted_cormat6b[order(melted_cormat6b$Var1), ]
melted_cormat6b

#subseting from correlation matrix
head(melted_cormat6b, 10)
melted_cormat6c=melted_cormat6b[1:8,]
melted_cormat6c

# Heatmap
library(ggplot2)
ggheatmap6a<-ggplot(data = melted_cormat6c, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Spearman Correlation") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 20, hjust = 0.7))+
  theme(axis.text.y = element_text(size=20))+
 coord_fixed()

#print(ggheatmap)

ggheatmap6b<-ggheatmap6a + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 12) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(1,1),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 12, barheight = 0.8,
                title.position = "top", title.hjust = 0.5,
                title.theme= element_text(size = 20, angle= 0)))

a1<-ggheatmap6b + ggtitle(expression(paste(italic('H. bilis'),"(pathobiont)-ASF-no DSS")))+ 
      labs(x="C3H/HeN - Cecal tissue associated bacteria")+ 
      theme(plot.title = element_text(size = 22))+
      theme(axis.title.x = element_text(size = 22))
a1


######################################################################
#subseting HbASF DSS for correlation matrix between pathobiont and ASF taxa in cecal tissue associated bacteria

str(data5)


#subset HbASF no DSS
data5
datasub7b=data5[c(9:17),]
datasub7b
sum(is.na(datasub7b))
str(datasub7b)
#now subset the quantitative variables out of HbASFdss
datasub7c=datasub7b[,-c(1:5)]
str(datasub7c)
plot(datasub7c)

#Pearson correlation and heat map HbASF no DSS

cormat7b<-round(cor(datasub7c, method="spearman", use = "complete.obs"),2)
heatmap(cormat7b)
head(cormat7b)

library(reshape2)
melted_cormat7b <- melt(cormat7b)
head(melted_cormat7b)

library(ggplot2)
ggplot(data = melted_cormat7b, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }

upper_tri7b<- get_upper_tri(cormat7b)
upper_tri7b


# Melt the correlation matrix
library(reshape2)
melted_cormat7c <- melt(upper_tri7b, na.rm = TRUE)
melted_cormat7c 
melted_cormat7c<-melted_cormat7c[order(melted_cormat7c$Var1), ]
melted_cormat7c

#subseting from correlation matrix
head(melted_cormat7c, 10)
melted_cormat7c=melted_cormat7c[1:8,]
melted_cormat7c

# Heatmap
library(ggplot2)
ggheatmap7a<-ggplot(data = melted_cormat7c, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Spearman Correlation") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 20, hjust = 0.7))+
  theme(axis.text.y = element_text(size=20))+
 coord_fixed()

#print(ggheatmap)

ggheatmap7b<-ggheatmap7a + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 12) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(1,1),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 12, barheight = 0.5,
                title.position = "top", title.hjust = 0.5,
                title.theme= element_text(size = 20, angle= 0)))

c1<-ggheatmap7b + ggtitle(expression(paste(italic('H. bilis'),"(pathobiont)-ASF-1.5% DSS")))+ 
      labs(x="C3H/HeN - Cecal tissue associated bacteria")+ 
      theme(plot.title = element_text(size = 22))+
      theme(axis.title.x = element_text(size = 22))
c1

library(gridExtra)
grid.arrange(a1,c1, nrow=2, clip=TRUE)
```

7) Antibiotic perturbation of ASF community

```{r, echo = TRUE}
dataab1<-read.csv("streptomycin.csv")
sum(is.na(dataab1)) #checking for NA
str(dataab1)
dataab1$Day=factor(dataab1$Day)
str(dataab1)
dataab2 <- dataab1[,-c(1:2)]
str(dataab2)
pcaab1<-prcomp(dataab2, scale= TRUE) 
summary(pcaab1)
pcaab1
plot(pcaab1, type='l', main="Scree plot")


PCi<-data.frame(pcaab1$x,Day=dataab1$Day)
ggplot(PCi,aes(x="PC1 (93.81%)",y="PC2 (2.78%)",col='Day'))+
   geom_point(size=3,alpha=0.5)+ #Size and alpha just for fun
   scale_color_manual(values = c("black","gray"))+ #your colors here
   theme_classic()

pcab1<-autoplot(prcomp(dataab2, scale=TRUE), data = dataab1, colour = 'Day', loadings= FALSE, loadings.label = FALSE, frame = TRUE, frame.type= 't', xlab="PC1 (93.81%)", ylab="PC2 (2.78%)")
pcab1
pcab1 + scale_fill_manual(values = c("yellow","gray"))+
  scale_color_manual(values = c("black","red")) +
  theme_bw()


#dataab1
#dat1<-dataab1[,-c(1:2, 4)]
pcnew<-prcomp(dataab2, scale= TRUE) 
summary(pcnew)
plot(pcnew, type='l', main="Scree plot")
pcab2<-autoplot(prcomp(dataab2, scale=TRUE), data = dataab1, colour = 'Day', loadings= FALSE, loadings.label = FALSE, frame = TRUE, frame.type= "t", xlab="PC1 (93.81%)", ylab="PC2 (2.78%)", label.size = 50, size = 8, label.n = 30)

pcab3<-pcab2 + scale_fill_manual(values = c("gray","gray"))+
  scale_color_manual(values = c("blue","red")) +
  theme_bw() 
pcab3+theme(axis.text=element_text(size=20, family="Times New Roman"),
        axis.title=element_text(size=20,face="bold", family="Times New Roman"),
        legend.text=element_text(size=20, family="Times New Roman"),
        legend.title=element_text(size=20, family="Times New Roman"))

####neomycin
dataneo<-read.csv("neomycin.csv")
sum(is.na(dataneo)) #checking for NA
str(dataneo)
dataneo$Day=factor(dataneo$Day)
str(dataneo)
dataneo1 <- dataneo[,-c(1:2)]
str(dataneo1)
pcaneo<-prcomp(dataneo1, scale= TRUE) 
summary(pcaneo)
pcaneo
plot(pcaneo, type='l', main="Scree plot")



pcab3<-autoplot(prcomp(dataneo1, scale=TRUE), data = dataneo, colour = 'Day', loadings= FALSE, loadings.label = FALSE, frame = TRUE, frame.type= "t", xlab="PC1 (91.39%)", ylab="PC2 (4.85%)", label.size = 50, size = 8, label.n = 30)

pcab4<-pcab3 + scale_fill_manual(values = c("gray","gray"))+
  scale_color_manual(values = c("blue","red")) +
  theme_bw() 
pcab4+theme(axis.text=element_text(size=20, family="Times New Roman"),
        axis.title=element_text(size=20,face="bold", family="Times New Roman"),
        legend.text=element_text(size=20, family="Times New Roman"),
        legend.title=element_text(size=20, family="Times New Roman"))

################################
fat1<-read.csv("fatsamples.csv")
sum(is.na(fat1)) #checking for NA
str(fat1)
fat2 <- fat1[,-c(1:2)]
str(fat2)
pcaf<-prcomp(fat2, scale= TRUE) 
summary(pcaf)
pcaf
plot(pcaf, type='l', main="Scree plot")



pcab3<-autoplot(prcomp(fat2, scale=TRUE), data = fat1, colour = 'Diet', loadings= FALSE, loadings.label = FALSE, frame = TRUE, frame.type= "t", xlab="PC1 (73.22%)", ylab="PC2 (14.86%)", label.size = 50, size = 8, label.n = 30)

pcab4<-pcab3 + scale_fill_manual(values = c("gray","gray"))+
  scale_color_manual(values = c("black","red")) +
  theme_bw() 
pcab4+theme(axis.text=element_text(size=20, family="Times New Roman"),
        axis.title=element_text(size=20,face="bold", family="Times New Roman"),
        legend.text=element_text(size=20, family="Times New Roman"),
        legend.title=element_text(size=20, family="Times New Roman"))

##############
h1<-read.csv("host.csv")
sum(is.na(h1)) #checking for NA
str(h1)
h2 <- h1[,-c(1:2)]
str(h2)
pcah<-prcomp(h2, scale= TRUE) 
summary(pcah)
pcah
plot(pcah, type='l', main="Scree plot")



pcab3<-autoplot(prcomp(h2, scale=TRUE), data = h1, colour = 'Genotype', loadings= FALSE, loadings.label = FALSE, frame = TRUE, frame.type= "t", xlab="PC1 (87.2%)", ylab="PC2 (7.39%)", label.size = 50, size = 8, label.n = 30)

pcab4<-pcab3 + scale_fill_manual(values = c("gray","gray"))+
  scale_color_manual(values = c("brown","black")) +
  theme_bw() 
pcab4+theme(axis.text=element_text(size=20, family="Times New Roman"),
        axis.title=element_text(size=20,face="bold", family="Times New Roman"),
        legend.text=element_text(size=20, family="Times New Roman"),
        legend.title=element_text(size=20, family="Times New Roman"))

##############
m1<-read.csv("mix.csv")
sum(is.na(m1)) #checking for NA
str(m1)
m2 <- m1[,-c(1:2)]
str(m2)
pcam<-prcomp(m2, scale= TRUE) 
summary(pcam)
pcam
plot(pcam, type='l', main="Scree plot")



pcab3<-autoplot(prcomp(m2, scale=TRUE), data = m1, colour = 'Mix', loadings= FALSE, loadings.label = FALSE, frame = TRUE, frame.type= "t", xlab="PC1 (70.4%)", ylab="PC2 (17.56%)", label.size = 50, size = 8, label.n = 30)

pcab4<-pcab3 + scale_fill_manual(values = c("gray","gray"))+
  scale_color_manual(values = c("blue","red")) +
  theme_bw() 
pcab4+theme(axis.text=element_text(size=20, family="Times New Roman"),
        axis.title=element_text(size=20,face="bold", family="Times New Roman"),
        legend.text=element_text(size=20, family="Times New Roman"),
        legend.title=element_text(size=20, family="Times New Roman"))

#################################################################
#ASF 356
library(ggplot2)
#install.packages("extrafont")
library(extrafont)
font_import()
#font_import(pattern="[T/t]imes New Roman")
loadfonts()
#theme(text=element_text(size=16,  family="TT Times New Roman"))
font_import(paths = NULL, recursive = TRUE, prompt = TRUE,pattern = NULL)
font_import(paths = "~/.fonts", pattern="Times New Roman")


ymix1<-read.csv("mix356.csv")
sum(is.na(mix1)) #checking for NA
str(mix1)

a<-ggplot(data = mix1, aes(x = Mix, y = Abundance)) +
  geom_boxplot(aes(x = rep(c(-3, 3), each = 7), group = Mix), fill = c('blue', 'red'), outlier.shape = 21, outlier.size = 6)+
  geom_point(aes(x = rep(c(-1, 1), each = 7)),size = 5)+
  geom_line(aes(x = rep(c(-1, 1), each = 7), group = ID)) +
  labs(x= " ", y = element_blank())
dt<-a+theme(axis.text=element_text(size=24, family="Times New Roman"),
            axis.title.x = element_text(size=30, face="bold", family="Times New Roman"),
            axis.title.y = element_text(size=26, face="bold", family="Times New Roman"))
#c<- dt + ylim(0,15)
#c
d<- dt+ labs(y=expression(bold(paste(Log [10], " of total gene copies/gram of cecal content")))) +
                 theme(axis.title.y=    element_text(colour="black",size=30, family="Times New Roman"))
d
e<- d + theme(axis.text.x=element_blank())
e
f<- e + ggtitle(expression(paste(title = "ASF 356 -",  italic(" Clostridium sp.")))) + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 32, face = "bold", family="Times New Roman"))
f
g<- f + annotate("text", x = 0, y = 9.1, label = "*", size= 30, family="Times New Roman")
g

##############################################################
#asf360
mix2<-read.csv("mix360.csv")
sum(is.na(mix2)) #checking for NA
str(mix2)

a1<-ggplot(data = mix2, aes(x = Mix, y = Abundance)) +
  geom_boxplot(aes(x = rep(c(-3, 3), each = 7), group = Mix), fill = c('blue', 'red'), outlier.shape = 21, outlier.size = 6)+
  geom_point(aes(x = rep(c(-1, 1), each = 7)), size = 5) +
  geom_line(aes(x = rep(c(-1, 1), each = 7), group = ID)) +
  labs(x= " ", y = element_blank())
dt1<-a1+theme(axis.text=element_text(size=24,family="Times New Roman"),
            axis.title.x = element_text(size=30, face="bold",family="Times New Roman"),
            axis.title.y = element_text(size=26, face="bold",family="Times New Roman"))
#c<- dt + ylim(0,15)
#c
d1<- dt1+ labs(y=expression(bold(paste(Log [10], " of total gene copies/gram of cecal content")))) +
                 theme(axis.title.y=    element_text(colour="black",size=30, family="Times New Roman"))
d1
e1<- d1 + theme(axis.text.x=element_blank())
e1
f1<- e1 + ggtitle(expression(paste(title = "ASF 360 -",  italic(" L. intestinalis")))) + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 32, face = "bold", family="Times New Roman"))
f1
g1<- f1 + annotate("text", x = 0, y = 4.7, label = "*", size= 30, family="Times New Roman")
g1

###############################################################
#asf361
mix3<-read.csv("mix361.csv")
sum(is.na(mix3)) #checking for NA
str(mix3)

a2<-ggplot(data = mix3, aes(x = Mix, y = Abundance)) +
  geom_boxplot(aes(x = rep(c(-3, 3), each = 7), group = Mix), fill = c('blue', 'red'), outlier.shape = 21, outlier.size = 6)+
  geom_point(aes(x = rep(c(-1, 1), each = 7)), size = 5) +
  geom_line(aes(x = rep(c(-1, 1), each = 7), group = ID)) +
  labs(x= " ", y = element_blank())
dt2<-a2+theme(axis.text=element_text(size=24, family="Times New Roman"),
            axis.title.x = element_text(size=30, face="bold", family="Times New Roman"),
            axis.title.y = element_text(size=26, face="bold", family="Times New Roman"))
#c<- dt + ylim(0,15)
#c
d2<- dt2+ labs(y=expression(bold(paste(Log [10], " of total gene copies/gram of cecal content")))) +
                 theme(axis.title.y=    element_text(colour="black",size=30, family="Times New Roman"))
d2
e2<- d2 + theme(axis.text.x=element_blank())
e2
f2<- e2 + ggtitle(expression(paste(title = "ASF 361 -",  italic(" L. murinus")))) + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 32, face = "bold", family="Times New Roman"))
f2
g2<- f2 + annotate("text", x = 0, y = 11.4, label = "*", size= 30, family="Times New Roman")
g2

###############################################################


#asf457
mix4<-read.csv("mix457.csv")
sum(is.na(mix4)) #checking for NA
str(mix4)

a3<-ggplot(data = mix4, aes(x = Mix, y = Abundance)) +
  geom_boxplot(aes(x = rep(c(-3, 3), each = 7), group = Mix), fill = c('blue', 'red'), outlier.shape = 21, outlier.size = 6)+
  geom_point(aes(x = rep(c(-1, 1), each = 7)), size = 5) +
  geom_line(aes(x = rep(c(-1, 1), each = 7), group = ID)) +
  labs(x= " ", y = element_blank())
dt3<-a3+theme(axis.text=element_text(size=24, family="Times New Roman"),
            axis.title.x = element_text(size=30, face="bold", family="Times New Roman"),
            axis.title.y = element_text(size=26, face="bold", family="Times New Roman"))
#c<- dt + ylim(0,15)
#c
d3<- dt3+ labs(y=expression(bold(paste(Log [10], " of total gene copies/gram of cecal content")))) +
                 theme(axis.title.y=    element_text(colour="black",size=30, family="Times New Roman"))
d3
e3<- d3 + theme(axis.text.x=element_blank())
e3
f3<- e3 + ggtitle(expression(paste(title = "ASF 457 -",  italic(" M. schaedleri")))) + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 32, face = "bold", family="Times New Roman"))
f3
g3<- f3 + annotate("text", x = 0, y = 10.2, label = "*", size= 30, family="Times New Roman")
g3

###############################################################

#asf492
mix5<-read.csv("mix492.csv")
sum(is.na(mix5)) #checking for NA
str(mix5)

a4<-ggplot(data = mix5, aes(x = Mix, y = Abundance)) +
  geom_boxplot(aes(x = rep(c(-3, 3), each = 7), group = Mix), fill = c('blue', 'red'), outlier.shape = 21, outlier.size = 6)+
  geom_point(aes(x = rep(c(-1, 1), each = 7)), size = 5) +
  geom_line(aes(x = rep(c(-1, 1), each = 7), group = ID)) +
  labs(x= " ", y = element_blank())
dt4<-a4+theme(axis.text=element_text(size=24, family="Times New Roman"),
            axis.title.x = element_text(size=30, face="bold", family="Times New Roman"),
            axis.title.y = element_text(size=26, face="bold", family="Times New Roman"))
#c<- dt + ylim(0,15)
#c
d4<- dt4+ labs(y=expression(bold(paste(Log [10], " of total gene copies/gram of cecal content")))) +
                 theme(axis.title.y=    element_text(colour="black",size=30, family="Times New Roman"))
d4
e4<- d4 + theme(axis.text.x=element_blank())
e4
f4<- e4 + ggtitle(expression(paste(title = "ASF 492 -",  italic(" E. plexicaudatum")))) + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 32, face = "bold", family="Times New Roman"))
f4
g4<- f4 + annotate("text", x = 0, y = 9.6, label = "*", size= 30, family="Times New Roman")
g4

###############################################################
#asf500
mix6<-read.csv("mix500.csv")
sum(is.na(mix6)) #checking for NA
str(mix6)

a5<-ggplot(data = mix6, aes(x = Mix, y = Abundance)) +
  geom_boxplot(aes(x = rep(c(-3, 3), each = 7), group = Mix), fill = c('blue', 'red'), outlier.shape = 21, outlier.size = 6)+
  geom_point(aes(x = rep(c(-1, 1), each = 7)), size = 5) +
  geom_line(aes(x = rep(c(-1, 1), each = 7), group = ID)) +
  labs(x= " ", y = element_blank())
dt5<-a5+theme(axis.text=element_text(size=24, family="Times New Roman"),
            axis.title.x = element_text(size=30, face="bold", family="Times New Roman"),
            axis.title.y = element_text(size=26, face="bold", family="Times New Roman"))
#c<- dt + ylim(0,15)
#c
d5<- dt5+ labs(y=expression(bold(paste(Log [10], " of total gene copies/gram of cecal content")))) +
                 theme(axis.title.y=    element_text(colour="black",size=30, family="Times New Roman"))
d5
e5<- d5 + theme(axis.text.x=element_blank())
e5
f5<- e5 + ggtitle(expression(paste(title = "ASF 500 -",  italic(" Pseudoflavonifractor sp.")))) + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 32, face = "bold", family="Times New Roman"))
f5
g5<- f5 + annotate("text", x = 0, y = 9.74, label = "*", size= 30, family="Times New Roman")
g5

###############################################################
#asf502
mix7<-read.csv("mix502.csv")
sum(is.na(mix7)) #checking for NA
str(mix7)

a6<-ggplot(data = mix7, aes(x = Mix, y = Abundance)) +
  geom_boxplot(aes(x = rep(c(-3, 3), each = 7), group = Mix), fill = c('blue', 'red'), outlier.shape = 21, outlier.size = 6)+
  geom_point(aes(x = rep(c(-1, 1), each = 7)), size = 5) +
  geom_line(aes(x = rep(c(-1, 1), each = 7), group = ID)) +
  labs(x= " ", y = element_blank())
dt6<-a6+theme(axis.text=element_text(size=24, family="Times New Roman"),
            axis.title.x = element_text(size=30, face="bold", family="Times New Roman"),
            axis.title.y = element_text(size=26, face="bold", family="Times New Roman"))
#c<- dt + ylim(0,15)
#c
d6<- dt6+ labs(y=expression(bold(paste(Log [10], " of total gene copies/gram of cecal content")))) +
                 theme(axis.title.y=    element_text(colour="black",size=30, family="Times New Roman"))
d6
e6<- d6 + theme(axis.text.x=element_blank())
e6
f6<- e6 + ggtitle(expression(paste(title = "ASF 502 -",  italic(" Clostridium sp.")))) + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 32, face = "bold", family="Times New Roman"))
f6
g6<- f6 + annotate("text", x = 0, y = 10.2, label = "*", size= 30, family="Times New Roman")
g6

###############################################################
#asf519

mix8<-read.csv("mix519.csv")
sum(is.na(mix8)) #checking for NA
str(mix8)

a7<-ggplot(data = mix8, aes(x = Mix, y = Abundance)) +
  geom_boxplot(aes(x = rep(c(-3, 3), each = 7), group = Mix), fill = c('blue', 'red'), outlier.shape = 21, outlier.size = 6)+
  geom_point(aes(x = rep(c(-1, 1), each = 7)), size = 5) +
  geom_line(aes(x = rep(c(-1, 1), each = 7), group = ID)) +
  labs(x= " ", y = element_blank())
dt7<-a7+theme(axis.text=element_text(size=24, family="Times New Roman"),
            axis.title.x = element_text(size=30, face="bold", family="Times New Roman"),
            axis.title.y = element_text(size=26, face="bold", family="Times New Roman"))
#c<- dt + ylim(0,15)
#c
d7<- dt7+ labs(y=expression(bold(paste(Log [10], " of total gene copies/gram of cecal content")))) +
                 theme(axis.title.y=    element_text(colour="black",size=30, family="Times New Roman"))
d7
e7<- d7 + theme(axis.text.x=element_blank())
e7
f7<- e7 + ggtitle(expression(paste(title = "ASF 519 -",  italic(" P. goldsteinii")))) + theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 32, face = "bold", family="Times New Roman"))
f7
g7<- f7 + annotate("text", x = 0, y = 10, label = "*", size= 30, family="Times New Roman")
g7
```


PCA plot TCR data all asf
```{r, echo=TRUE}
#PCA plot TCR data all asf
#setwd("~/Documents/pathobiont paper/assembly experiment/assembly 2/all ASF")
#allasf1 <- read_csv("allasfTCR.csv")
#library(readr)
#dataset <- read_csv(NULL)
allasf1 <- read_csv("~/Documents/pathobiont paper/assembly experiment/assembly 2/all asf/allasfTCR.csv")
View(allasf1)
sum(is.na(allasf1)) #checking for NA
str(allasf1)
asf2 <- allasf1[,-(1)]
str(asf2)
pcam<-prcomp(asf2, scale= TRUE) 
summary(pcam)
pcam
plot(pcam, type='l', main="Scree plot")

autoplot(prcomp(asf2), data= allasf1, colour = 'DSS')

autoplot(prcomp(asf2, scale=TRUE), data = allasf1, colour = 'DSS', loadings= TRUE, loadings.label = TRUE, loadings.colour = 'black', frame = TRUE, frame.type= "t", xlab="PC1 (60.36%)", ylab="PC2 (12.04%)", label.size = 50, size = 8, label.n = 30)

#pcab4<-a + scale_fill_manual(values = c("gray","gray"))+
  #scale_color_manual(values = c("black","red")) +
 # theme_bw() 
#pcab4+theme(axis.text=element_text(size=20, family="Times New Roman"),
        #axis.title=element_text(size=20,face="bold", family="Times New Roman"),
       # legend.text=element_text(size=20, family="Times New Roman"),
       # legend.title=element_text(size=20, family="Times New Roman"))

#################################################################################################
#PCA plot TCR data all asf minus 356
asf3 <- read_csv("~/Documents/pathobiont paper/assembly experiment/assembly 2/all asf/asfminus356.csv")
View(asf3)
#asf3 <- read_csv("asfminus356.csv")
sum(is.na(asf3)) #checking for NA
str(asf3)
asf4 <- asf3[,-(1)]
str(asf4)
pcam1<-prcomp(asf4, scale= TRUE) 
summary(pcam1)
pcam1
plot(pcam1, type='l', main="Scree plot")

autoplot(prcomp(asf4, scale=TRUE), data = asf3, colour = 'DSS', loadings= TRUE, loadings.label = TRUE, loadings.colour = 'black', frame = TRUE, frame.type= "t", xlab="PC1 (70.03%)", ylab="PC2 (11.48%)", label.size = 50, size = 8, label.n = 30)


#################################################################################################
#PCA plot TCR data all asf minus 356 and 361
asf5 <- read_csv("~/Documents/pathobiont paper/assembly experiment/assembly 2/all asf/asfminus356and361.csv")
View(asf5)
sum(is.na(asf5)) #checking for NA
str(asf5)
asf6 <- asf5[,-(1)]
str(asf6)
pcam2<-prcomp(asf6, scale= TRUE) 
summary(pcam2)
pcam2
plot(pcam2, type='l', main="Scree plot")

autoplot(prcomp(asf6, scale=TRUE), data = asf5, colour = 'DSS', loadings= TRUE, loadings.label = TRUE, loadings.colour = 'black', frame = TRUE, frame.type= "t", xlab="PC1 (74.96%)", ylab="PC2 (8.64%)", label.size = 50, size = 8, label.n = 30)

```

